\documentclass[letterpaper,11pt]{article}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{fullpage}
\usepackage{ifthen}
\usepackage{subfigure}
\usepackage{epic}
\usepackage{authblk}
\usepackage{textcomp}
\usepackage[small]{caption}


\usepackage[hypertexnames=false,colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[numbers,comma,square,sort&compress]{natbib}
\usepackage[letterpaper,text={7in,9in},centering]{geometry}


\usepackage{color}
\usepackage{titlesec}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1.0ex plus0.2ex minus0.2ex}
\renewcommand{\baselinestretch}{1.1}
\graphicspath{{eps/}{pdf/}}
%\setcaptionmargin{0.25in}
\def\captionfont{\itshape\small}
\def\captionlabelfont{\upshape\small}

\renewcommand{\labelenumi}{(\roman{enumi})}

\newcommand{\bqq}{\begin{equation}}
\newcommand{\eqq}{\end{equation}}
\newcommand{\bqs}{\begin{equation*}}
\newcommand{\eqs}{\end{equation*}}

\newcommand{\C}{\mathbb{C}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}} 
\newcommand{\Z}{\mathbb{Z}}

\newcommand{\rme}{\mathrm{e}}
\newcommand{\rmi}{\mathrm{i}}
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\rmo}{{\scriptstyle\mathcal{O}}}
\newcommand{\rmO}{\mathcal{O}}
\newcommand{\eps}{\varepsilon}

\numberwithin{equation}{section}

\newenvironment{Hypothesis}[1]%
  {\begin{trivlist}\item[]{\bf Hypothesis #1 }\em}{\end{trivlist}}

\renewcommand{\arraystretch}{1.25}


% Define Theorem Styles ----------------------------------
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{main}[theorem]{Main Result}
\newtheorem{rmk}[theorem]{rmk}


\newcommand{\etal}{\textit{et al.}\ }

\newcommand{\greg}[1]{%
  {\color{blue}\textbf{Greg:} #1}%
 }
 
\newcommand{\arnd}[1]{%
  {\color{red}\textbf{Arnd:} #1}%
 }

\newenvironment{Proof}[1][.]%
 {\begin{trivlist}\item[]\textbf{Proof#1 }}%
 {\hspace*{\fill}$\rule{0.3\baselineskip}{0.35\baselineskip}$\end{trivlist}}

\renewcommand\labelitemi{$\bullet$}


\title{List of changes}
\author{author}
\begin{document}
List of changes 
``Bifurcation to coherent structures in nonlocally coupled systems''

I did not find any major changes that distorted the equations, formulas, etc. The changes are mainly in style:

\begin{itemize}

\item ``Sections '' are being changed to ``Sects''. Example: line 33, line 34. One place where I found a little bit incoherence is line 246, right after ``Sect 3.'' The sentence started with ``Section 4'', maybe it should be changed to ``Sects'' for consistency?

\item In the title for a section or a paragraph, a dash has been changed into a colon, and the first letter of each word has been capitalized, also the period at the end of the title is deleted. Example: line 36: ``\textbf{ Local Coupling: Result}'', which originally in our submitted paper is ``\textbf{ Local coupling --- results.}''


\item The paragraph for acknowledgment is deleted. (after line 262)

\item The title for ``remark'' is now not in bold font (line 143, line 166, and line 453)

\item The reference to ``equations'' has been changed to ``Eq.'' Example: line 244 ``See Eq.(3.2)'' which originally is ``See equation (3.2)'' .

\item The proof environment is changed, now all the proof end with an empty box instead of a solid black one.

\item The labeling for Theorem $1$ has been change to Theorem $1.3$ (line 213, line 568 and line 569)


\item This one is a typo I found in our original paper, in line 148, we had $\tilde{M}(y) = \langle e^*, \tilde{K}(x)e\rangle$, the $x$ should be changed to $y$, same change should apply to the formula for $M(y)$ immediately behind.

\item Reference 13. Now appears at Transactions AMS

\item
 \end{itemize}

Tianyu Tao and Arnd Scheel
\end{document}